Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
Updated log/output files and removed need for corpussize.tex
Those variables are now updated by examining the output of analyse; latest
camfort includes a 'linesTotal' output as well.

\include{results}
\include{corpussize}

@@

We define a semantic model for our stencil specification language.
This model has a number of purposes: (1) it is used in the inference,
checking, and program synthesis algorithms (introduced in
Section~\ref{sec:analysis}); (2) gives a basis for the equational
theory and approximations of the previous section; and (3) can be used
to guide correct implementations. The model is a denotational
semantics, in terms of sets of vectors which we call \emph{index
  schemes}. We introduce first the notion of indexing schemes
and \emph{unification} which gives the domain of our model
and forms the basis of the rest of the algorithsm for our
specificaiton. We then define the denotational model.

@@

\begin{definition}[Schematic]
The partial function $\textsf{schematic}$ maps 
source-language indexing terms $(e_1, \ldots, e_n)$
into $n$-dimensional index schemes 
$\in (\domainVal)^n$, defined:
%
\begin{align*}
\mathsf{schematic}(e_1, \ldots, e_n) & = 
[\downarrow\!e_1 \ldots \downarrow\!e_n ] 
\quad \textit{iff} \; \forall i . \downarrow\!e_i \neq \bot 
\end{align*}
%
The $\downarrow$ operator is a partial\footnote{We represent
  partiality explicitly in our types with the set $A + \bot$.} function 
 $\downarrow : \textit{expr} \rightarrow (\domainVal + \bot)$
which maps each individal indexing expression to a component of
the indexing scheme, defined: 
%%
\begin{align*}
\downarrow\!e
 & =  \begin{cases}
a & e \equiv i + a \; \wedge \; \mathsf{neigh}(i + a) \\
-a & e \equiv i - a \; \wedge \; \mathsf{neigh}(i - a) \\
\infty & \textit{$\mathsf{IV}(e) = \emptyset$} \\
\bot   & \textit{otherwise}
\end{cases}
\end{align*}
%%
where $\mathsf{IV}(e)$ is the set of free induction variables
appearing in an expression, and $\neigh{}$ classifies expressions which 
are constant offsets from an induction variable
(Defn.~\ref{def:neighbour}). In the third case, 
if the expression is not a neighbourhood index but is not
a relative index either (\ie{} is not defined in terms
of an induction variable) then it is mapped to $\infty$, otherwise
$\downarrow\!e$ is undefined. The $\mathsf{schematic}$ function
is undefined if $\downarrow$ of any of its components $e_i$ is
undefined.

>>>>

\include{results}

@@

We define a semantic model for our stencil specification language.
This model has a number of purposes: (1) it is used in the inference,
checking, and program synthesis algorithms (introduced in
Section~\ref{sec:analysis}); (2) gives a basis for the equational
theory and approximations of the previous section; and (3) can be used
to guide correct implementations. The model is a denotational
semantics, in terms of sets of vectors which we call \emph{index
  schemes}. We introduce first the notion of indexing schemes
and \emph{unification} which gives the domain of our model
and forms the basis of the rest of the algorithsm for our
specificaiton. We then define the denotational model

@@

\begin{definition}[Schematic]
The partial function $\textsf{schematic}$ maps 
source-language indexing terms $(e_1, \ldots, e_n)$
into $n$-dimensional indexing schemes 
($\in \domainVal^n$), defined:
%
\begin{align*}
\mathsf{schematic}(e_1, \ldots, e_n) & = 
[\downarrow\!e_1 \ldots \downarrow\!e_n ] 
\quad \textit{iff} \; \forall i . \downarrow\!e_i \neq \bot 
\end{align*}
%
The $\downarrow$ operator is a partial\footnote{We represent
  partiality explicitly in our types with the set $A + \bot$.} function 
 $\downarrow : \textit{expr} \rightarrow (\domainVal + \bot)$
which maps each individal indexing expression to a component of
the indexing scheme, defined: 
%%
\begin{align*}
\downarrow\!e
 & =  \begin{cases}
a & e \equiv i + a \; \wedge \; \mathsf{neigh}(i + a) \\
-a & e \equiv i - a \; \wedge \; \mathsf{neigh}(i - a) \\
\infty & \textit{$\mathsf{IV}(e) = \emptyset$} \\
\bot   & \textit{otherwise}
\end{cases}
\end{align*}
%%
where $\mathsf{IV}(e)$ is the set of free induction variables
appearing in an expression, and $\neigh{}$ classifies expressions which 
are constant offsets from an induction variable
(Defn.~\ref{def:neighbour}). In the third case, 
if the expression is not a neighbourhood index but is not
a relative index either (\ie{} is not defined in terms
of an induction variable) then it is mapped to $\infty$, otherwise
$\downarrow\!e$ is undefined. The $\mathsf{schematic}$ function
is undefined if $\downarrow$ of any of its components $e_i$ is
undefined.
